---
title: "Data Analysis Master Thesis 2021"
author: "Pernille Berg Lassen"
date: "5/2/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---
The analysis consits of:
1. Data cleaning
2. Sparseness calculation
3. Preparing data to analysis in Matlab (rocScore calulation from gbvs)
4. Analysis on Matlab data (outcome of gbvs)
5.


Steps: 

1 Preliminary data exploration:

1.a Qualitity checks of the eye-tracking data
  How? Averaged across all participants? How to avoid a center-bias? (All data will be    clustered acround the center)
  
1.b Behavioral data
  Demographics: Age (mean, range, SD)
  General art-interest (between groups and across entire participant pool)
  Familiarity - how familiar were the artworks to the participants? Confounding?
  
  
2 Vizualitions (Both behavioral and eye-tracking data)
  Behavioral: Bar plots
  ET: Heat maps and scan paths
  
Scaling the ET data (viewing times are varied)


3 Defining AOI's/ROI's/Clusters
  Define AOI based on saliency maps (purely bottom-up) 
  Define clusters from the fixation data - dbscan (Davies et al.)
  Evt. define AOI based on Arnheim
  
4 Models
  4.a Behavioral data: (g)lmer
     Does condiiton predict ratings (understanding and appreciaiton)?
     Does rating predict artist/art-genre?
       Any artist/art-genre that recieved hihger/lower ratings?
     Does art interest predict ratings? A trend across artist/art-genre?
     Does familiarity (if relevant - depends on the overall familiarity level)?
     
  Check correlation between the questions - collapse or nah?
  
  4.b ET: glmer
    NB: a sequential dimensions - first five fixations (more bottom-up) vs. the rest        (more top-down)
    Does duration of fixation + number of fixations predict condition? (Or the other way     around)?
    Does time spent in AOI predict condition? (or the other way around)?
    Does time to first fixation in AOI's predict condition? (or the other way around)?
    Does total viewing time (scaled) predict condition/artist/art-genre? 
    
5 Saliency algoritm
  ET: looking at the effect of saliency
  NB: The whole dataset (averaged across participants) vs. fixations only in   clusters   (so AOI defined from the fixations)?)
  
  First five fixations vs. the rest of the fixations. 
  
  ROC and AUC - accuracy
  
  Saliency maps + three conspicuity maps (color, intensity and orientation)
  
6 Model evaluation
  Cross-validation of models - investigate predictive power as well as explanatory
  
Transition behavior between clusters?

###Loading packages
```{r}
library(pacman)
p_load(devtools,tidyverse,lmerTest,data.table,ggpubr,caret,lme4,png,dbscan,gtools, factoextra)
library(ggimage)
#library(edfReader)
```


```{r}
#Load data
BehaveDat = read.csv("DataBsC/BehavioralData_New.csv") #<-- using data from the Bachelor to test code
BehaveDat = subset(BehaveDat, select = -c(X))

SacDat = read.csv("DataBsc/SaccadesData_New.csv",header = T)
SacDat = subset(SacDat, select = -c(X))
SacDat = subset(SacDat, select = -c(Number_sac))
SacDat = subset(SacDat,SacDat$Duration < 80) #Removing artifacts

FixDat = read.csv("DataBsC/FixationsData_New.csv", header = T)
FixDat = subset(FixDat, select = -c(X))
FixDat = subset(FixDat, select = -c(Number_fix))
FixDat = subset(FixDat,FixDat$Duration > 200) #Removing artifacts

count = group_by(FixDat,image,ID) %>% summarize(Number_fix=n())
countSac = group_by(SacDat,image,ID) %>% summarize(Number_sac=n())
Fix_df = plyr::join(FixDat,count)
Sac_df = plyr::join(SacDat,countSac)
Fix_df$PositionY = round((901-Fix_df$PositionY),2) #Data was flipped - make sure to check if this is also the case for new data

#Renaming images - change accordingly depending on stimulus names
Fix_df$image = str_replace_all(Fix_df$image,"images_",'')
Fix_df$image = str_replace_all(Fix_df$image,"\\\\",'')
Fix_df$image = str_replace_all(Fix_df$image,"rothko",'')
Fix_df$image = str_replace_all(Fix_df$image,"pollock",'')
Fix_df$image = str_replace_all(Fix_df$image,"schiele",'')
Fix_df$image = str_replace_all(Fix_df$image,"chagall",'')
Fix_df$image = str_replace_all(Fix_df$image,".png",'')

#remove(FixDat)
#remove(SacDat)
#remove(count)
#remove(countSac)

#First 10 fixations on each image
Fix_df_10Fix <-
Fix_df %>% 
  group_by(ID,image) %>% 
  filter(row_number()==1:10)

#Recap:
#Fix_df = full dataset
#Fix_df_10Fix = first 10 fixations on each image for each participants

#merge with results from sparseness analysis:
sparsenessResults <- read.csv('SparsenessResults.csv')
sparsenessResults <- subset(sparsenessResults, select = -c(X))
Fix_df_10Fix <- merge(Fix_df_10Fix,sparsenessResults)
Fix_df_10Fix <- Fix_df_10Fix[order(Fix_df_10Fix[,2], Fix_df_10Fix[,18]),]
```

Vizualizations and preliminary data-exploration

```{r}
#Demographics

Dat_grouped = group_by(BehaveDat,ID,gender,condition,age) %>% summarize()

sum(Dat_grouped$gender == 'Female' & Dat_grouped$condition == 1) 
sum(Dat_grouped$gender == 'Female' & Dat_grouped$condition == 0) 
sum(Dat_grouped$gender == 'Male' & Dat_grouped$condition == 1) 
sum(Dat_grouped$gender == 'Male' & Dat_grouped$condition == 0)
round(mean(Dat_grouped$age),2)
round(sd(Dat_grouped$age),2)
round(mean(Dat_grouped$age[Dat_grouped$condition == 1]),2)
round(sd(Dat_grouped$age[Dat_grouped$condition == 1]),2)
round(mean(Dat_grouped$age[Dat_grouped$condition == 0]),2)
round(sd(Dat_grouped$age[Dat_grouped$condition == 0]),2)

#Image familarity 

Image_grouped = group_by(BehaveDat, ID, image, q7, artist, genre) %>% summarize()
img_fam = subset(Image_grouped,Image_grouped$q7 == 'yes')
img_fam = group_by(img_fam,image, artist, genre)  %>% summarize(Number_yes=n())
img_fam$Number_yes = sort(img_fam$Number_yes, decreasing = T)

summary(img_fam$artist) 
summary(img_fam$genre)

sum(img_fam$Number_yes[img_fam$artist == 'chagall']) #change with relevant artist names
sum(img_fam$Number_yes[img_fam$artist == 'schiele'])
sum(img_fam$Number_yes[img_fam$artist == 'rothko'])
sum(img_fam$Number_yes[img_fam$artist == 'pollock'])

sum(img_fam$Number_yes[img_fam$genre == 'fig'])
sum(img_fam$Number_yes[img_fam$genre == 'abstract'])


#Art interest
art_interest <- BehaveDat %>% #summarizing results from art interest questionaire
  group_by(ID) %>%
  summarize(
    q8 = q8[1],
    q9 = q9[1],
    q10 = q10[1],
    q11 = q11[1],
    condition = condition[1]
  )

#How many participants have taken art-classes?

length(art_interest$ID[art_interest$q11 == "yes" & art_interest$condition == 1])
length(art_interest$ID[art_interest$q11 == "yes" & art_interest$condition == 0])

art_interest$condition = as.factor(art_interest$condition)

art_interest$condition = plyr::revalue(art_interest$condition, c("1"= "Experts", "0"= "Non-Experts"))

all_part <- ggplot(art_interest, aes(x = q8)) +
  geom_bar(fill = "#99CCFF") +
  xlab("Ratings: Question X") +
  ylab("Participant counts") +
  theme_minimal()
  #How to change the values on the y-axis?

#Bar plots
bar_plot <- ggplot(art_interest, aes(x = q8)) + 
  geom_bar(fill = "#99CCFF") + 
  facet_wrap(~condition) + 
  xlab("Ratings: Question X") + 
  ylab("Partcipant counts") + 
  theme_minimal()

box_plot <- ggplot(art_interest,aes(y=q9,x=condition)) +
  geom_boxplot(color = "#336699", fill = "#6699CC") +
  xlab("Condition") +
  ylab("Rating") +
  ggtitle("Question X") + 
  coord_cartesian(ylim = c(1, 7)) +
  theme_minimal()

#Leaving an axis label blank: theme(axis.title.y = element_blank())

ggarrange(all_part,bar_plot) #what plots to display next to one another?

```

Testing art-interest

```{r}
#Mean and SD
art_interest %>%
  group_by(condition) %>%
  summarize(
    mean_q8 = round(mean(q8),2),
    sd_q8 = round(sd(q8),2),
    mean_q9 = round(mean(q9),2),
    sd_q9 = round(sd(q9),2),
    mean_q10 = round(mean(q10),2),
    sd_q10 = round(sd(q10),2)
  )

#testing assumptions - what to test?

model <- glm(condition ~ q8, family = 'binomial', art_interest) #one model per question or one model with all questions?
summary(model)


```

Scanpaths and heatmaps

```{r}
#Acessing quality of ET data?
#Subsetting dataframe to make heatmaps for 4 chosen images

img <- png::readPNG('DataBsC/heatmaps_scanpaths_images/screenshot_fig11.png')
g <- grid::rasterGrob(img, interpolate = T)

jet.colors <- colorRampPalette(c("#00007F", "blue", "#007FFF", "cyan", "#7FFF7F", "yellow", "#FF7F00", "red", "#7F0000"))

#Participant 1
heatmap_P1 <- ggplot(subset(Fix_df, ID==1 & image=='images_schiele\\fig_11.png'),aes(x = PositionX, y = PositionY)) +
  xlim(0,1600) +
  ylim(0, 900) +
  annotation_custom(g, xmin=-Inf, xmax=Inf, ymin=-0, ymax=900) +
  stat_density2d(geom="raster", aes(fill=..density.., alpha=sqrt(sqrt(..density..))), contour=FALSE, n=1000) +
scale_alpha(range = c(0.1, 0.6)) + scale_fill_gradientn(colours = jet.colors(10), trans='sqrt')

#Participant 2
heatmap_P2 <- ggplot(subset(Fix_df, ID==2 & image=='images_rothko\\abstract_6.png'),aes(x = PositionX, y = PositionY)) +
  xlim(0,1600) +
  ylim(0, 900) +
  annotation_custom(g, xmin=-Inf, xmax=Inf, ymin=-0, ymax=900) +
  stat_density2d(geom="raster", aes(fill=..density.., alpha=sqrt(sqrt(..density..))), contour=FALSE, n=1000) +
scale_alpha(range = c(0.1, 0.6)) + scale_fill_gradientn(colours = jet.colors(10), trans='sqrt')

#All participants
heatmap <- ggplot(subset(Fix_df, image=='images_schiele\\fig_11.png'),aes(x = PositionX, y = PositionY)) +
  xlim(0,1600) +
  ylim(0, 900) +
  annotation_custom(g, xmin=-Inf, xmax=Inf, ymin=-0, ymax=900) +
  stat_density2d(geom="raster", aes(fill=..density.., alpha=sqrt(sqrt(..density..))), contour=FALSE, n=1000) +
scale_alpha(range = c(0.1, 0.6)) + scale_fill_gradientn(colours = jet.colors(10), trans='sqrt')

averaged_heatmaps <- Fix_df %>%
  group_by(image) %>%
  mutate(Counter = sequence(rle(ID)$lengths)) %>%
  ungroup() %>%
  group_by(image, Counter) %>%
  summarize(
    PositionX = median(PositionX),
    PositionY = median(PositionY)
  )

aveHM <-
  ggplot(subset(averaged_heatmaps,image == "images_schiele\\fig_11.png"),aes(x =1601-PositionX, y = PositionY)) +
  xlim(0,1600) +
  ylim(0,900) +
  annotation_custom(g,xmin=-Inf, xmax=Inf, ymin=-0, ymax=900) +
  stat_density2d(geom="raster", aes(fill=..density.., alpha=sqrt(sqrt(..density..))), contour=FALSE, n=1000) + scale_alpha(range = c(0.1, 0.6)) +
  scale_fill_gradientn(colours = jet.colors(10), trans='sqrt') + ggtitle("All Participants")

#Remove fixations that is not on the stimulus?

```

Cluster definition using DBSCAN

```{r}
#Testing dbscan

#Dbscan should be on full data set?

averaged_full_data_C1 <- subset(Fix_df, Fix_df$condition == 1) %>%
  group_by(image) %>%
  mutate(Counter = sequence(rle(ID)$lengths)) %>%
  ungroup() %>%
  group_by(image, Counter) %>%
  summarize(
    PositionX = median(PositionX),
    PositionY = median(PositionY)
  )

averaged_full_data_C0 <- subset(Fix_df, Fix_df$condition == 0) %>%
  group_by(image) %>%
  mutate(Counter = sequence(rle(ID)$lengths)) %>%
  ungroup() %>%
  group_by(image, Counter) %>%
  summarize(
    PositionX = median(PositionX),
    PositionY = median(PositionY)
  )
#test <- subset(test, select = c(PositionX,PositionY)) #selecting fixations position only
#test <- as.matrix(test) #dbscan works with matrices
#kNNdistplot(test,k=4) + abline(h = 60, col = "red", lty = 2) #use knn distance plot to determine optimal eps value - look for where the data changes significantly (from linear to exponential)
#db <- dbscan(test, eps = 40) #run cluster analysis


#Generate kNN distance plots to determine optimal eps value - look for where the data changes significantly
for(i in unique(averaged_full_data_C0$image)){
  data <- subset(averaged_full_data_C0, image == i)
  data <- subset(data, select = c(PositionX, PositionY))
  matrix_data <- as.matrix(data)
  file = i
  print(kNNdistplot(matrix_data,k=4))
  #assign(paste("kNN_",file,sep = ""),distplot)
}

#Run cluster analysis using dbscan and save outcome
#Need to be done: add the optimal eps value for each image
for(i in unique(averaged_full_data_C0$image)){
  data <- subset(averaged_full_data_C0, image == i)
  data <- subset(data, select = c(PositionX, PositionY))
  matrix_data <- as.matrix(data)
  file = i
  db <- dbscan(matrix_data, eps = 30)
  assign(paste("db_",file,sep = ""),db)
}

#list_of_eps_values = (10,10)

subset_data <- as.matrix(subset(averaged_full_data_C0,  averaged_full_data_C0$image == "abstract_1", select = c(PositionX, PositionY)))

db_test <- dbscan(matrix_data,eps = )

plot  <-  fviz_cluster(db_abstract_1, subset_data, stand = FALSE, geom = 'point') +
  xlim(0,1600) +
  ylim(0,900)

img = "DataBsC/heatmaps_scanpaths_images/screenshot_fig1.png"

ggbackground(plot,img) #yeah that doesn't work   

bkg_img <- png::readPNG("DataBsC/heatmaps_scanpaths_images/screenshot_fig1.png")
pairs(test, col = db$cluster + 1L) #clusters seperated by axis
plot(test, col = db$cluster + 1L) #clusters = red, noise points = black
limits <- par() 
rasterImage(bkg_img, limits$usr[1], limits$usr[3], limits$usr[2], limits$usr[4]) 
points(test[db$cluster==0,], pch = 3, col = "grey")

img <- png::readPNG('DataBsC/heatmaps_scanpaths_images/screenshot_abs1.png')
g <- grid::rasterGrob(img, interpolate = T)

test <- as.data.frame(test)

plot_2 <- ggplot(test, aes(x = PositionX, y = PositionY)) +
  xlim(0,1600) +
  ylim(0,900) +
  annotation_custom(g, xmin=-0, xmax=1600, ymin=-0, ymax=900) +
  geom_point()

#Prettier visualization - How to add a background image?
plot  <-  fviz_cluster(db, test, stand = FALSE, geom = "point", main = "Cluster formation in 'Number 8' by Jackson Pollock") +
  xlim(0,1600) +
  ylim(0,900)
```

