---
title: "Data Analysis Master Thesis 2021"
author: "Pernille Berg Lassen"
date: "5/2/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---
The analysis consits of:
1. Data cleaning and preliminary data exploration
2. Sparseness calculation
3. Preparing data to analysis in Matlab (rocScore calulation from gbvs)
4. Cluster definition using dbscan - vizualisations 
5. Analysis on Matlab data (outcome of gbvs) - glmer models and visualizations
6. AOI analysis - 1) from sal maps, 2) from dbscan, 3) from theory
7. Transition matrices 


Steps: 

1 Preliminary data exploration:

1.a Qualitity checks of the eye-tracking data
  How? Averaged across all participants? How to avoid a center-bias? (All data will be    clustered acround the center)
  
1.b Behavioral data
  Demographics: Age (mean, range, SD)
  General art-interest (between groups and across entire participant pool)
  Familiarity - how familiar were the artworks to the participants? Confounding?
  
  
2 Vizualitions (Both behavioral and eye-tracking data)
  Behavioral: Bar plots
  ET: Heat maps and scan paths
  
Scaling the ET data (viewing times are varied)


3 Defining AOI's/ROI's/Clusters
  Define AOI based on saliency maps (purely bottom-up) 
  Define clusters from the fixation data - dbscan (Davies et al.)
  Evt. define AOI based on Arnheim
  
4 Models
  4.a Behavioral data: (g)lmer
     Does condiiton predict ratings (understanding and appreciaiton)?
     Does rating predict artist/art-genre?
       Any artist/art-genre that recieved hihger/lower ratings?
     Does art interest predict ratings? A trend across artist/art-genre?
     Does familiarity (if relevant - depends on the overall familiarity level)?
     
  Check correlation between the questions - collapse or nah?
  
  4.b ET: glmer
    NB: a sequential dimensions - first five fixations (more bottom-up) vs. the rest        (more top-down)
    Does duration of fixation + number of fixations predict condition? (Or the other way     around)?
    Does time spent in AOI predict condition? (or the other way around)?
    Does time to first fixation in AOI's predict condition? (or the other way around)?
    Does total viewing time (scaled) predict condition/artist/art-genre? 
    
5 Saliency algoritm
  ET: looking at the effect of saliency
  NB: The whole dataset (averaged across participants) vs. fixations only in   clusters   (so AOI defined from the fixations)?)
  
  First 10 fixations vs. the rest of the fixations. 
  
  ROC and AUC - accuracy
  
  Saliency maps + three conspicuity maps (color, intensity and orientation)
  
6 Model evaluation
  Cross-validation of models - investigate predictive power as well as explanatory
  
Transition behavior between clusters?

###Loading packages
```{r}
library(pacman)
p_load(devtools,tidyverse,lmerTest,data.table,ggpubr,caret,lme4,png,dbscan,gtools,wesanderson)
library(factoextra)
library(ggforce)
library(concaveman)
library(RColorBrewer)
#library(edfReader)
```


```{r}
#Load data
BehaveDat = read.csv("DataBsC/BehavioralData_New.csv") #<-- using data from the Bachelor to test code
BehaveDat = subset(BehaveDat, select = -c(X))

Fix_df = read.csv('Old_fixation_data.csv')
Fix_df = subset(Fix_df, select = -c(X))

Fix_df_10Fix = read.csv('Old_data_10Fix.csv')
Fix_df_10Fix = subset(Fix_df_10Fix, select = -c(X))

#Recap:
#Fix_df is the full dataset with all fixations
#Fix_df_10Fix includes only the first 10 fixations on each image for each participant

#Merge with results from sparseness analysis:
sparsenessResults <- read.csv('SparsenessResults.csv')
sparsenessResults <- subset(sparsenessResults, select = -c(X))
Fix_df_10Fix <- merge(Fix_df_10Fix,sparsenessResults)
Fix_df_10Fix <- Fix_df_10Fix[order(Fix_df_10Fix[,2], Fix_df_10Fix[,18]),]

#rm(sparsenessResults)

#Reading in AUC scores - full set
auc_df <- read.csv('AUC_scores_nowWithAllPart.csv')
auc_df <- merge(auc_df,sparsenessResults)
auc_df <- subset(auc_df, select = -c(X))
auc_df <- auc_df[order(auc_df[,1], auc_df[,2],auc_df[,4]),]


#Reading in AUC scores - five first seconds (missing P1 and P13)
auc_5s <- read.csv('AUC_scores_5sec.csv')
auc_5s <- merge(auc_5s,sparsenessResults)
auc_5s <- subset(auc_5s, select = -c(X))
auc_5s <- auc_5s[order(auc_5s[,1], auc_5s[,2],auc_5s[,3]),]

```

Vizualizations and preliminary data-exploration

```{r}
#Demographics

Dat_grouped = group_by(BehaveDat,ID,gender,condition,age) %>% summarize()

sum(Dat_grouped$gender == 'Female' & Dat_grouped$condition == 1) 
sum(Dat_grouped$gender == 'Female' & Dat_grouped$condition == 0) 
sum(Dat_grouped$gender == 'Male' & Dat_grouped$condition == 1) 
sum(Dat_grouped$gender == 'Male' & Dat_grouped$condition == 0)
round(mean(Dat_grouped$age),2)
round(sd(Dat_grouped$age),2)
round(mean(Dat_grouped$age[Dat_grouped$condition == 1]),2)
round(sd(Dat_grouped$age[Dat_grouped$condition == 1]),2)
round(mean(Dat_grouped$age[Dat_grouped$condition == 0]),2)
round(sd(Dat_grouped$age[Dat_grouped$condition == 0]),2)

#Image familarity 

Image_grouped = group_by(BehaveDat, ID, image, q7, artist, genre) %>% summarize()
img_fam = subset(Image_grouped,Image_grouped$q7 == 'yes')
img_fam = group_by(img_fam,image, artist, genre)  %>% summarize(Number_yes=n())
img_fam$Number_yes = sort(img_fam$Number_yes, decreasing = T)

summary(img_fam$artist) 
summary(img_fam$genre)

sum(img_fam$Number_yes[img_fam$artist == 'chagall']) #change with relevant artist names
sum(img_fam$Number_yes[img_fam$artist == 'schiele'])
sum(img_fam$Number_yes[img_fam$artist == 'rothko'])
sum(img_fam$Number_yes[img_fam$artist == 'pollock'])

sum(img_fam$Number_yes[img_fam$genre == 'fig'])
sum(img_fam$Number_yes[img_fam$genre == 'abstract'])


#Art interest
art_interest <- BehaveDat %>% #summarizing results from art interest questionaire
  group_by(ID) %>%
  summarize(
    q8 = q8[1],
    q9 = q9[1],
    q10 = q10[1],
    q11 = q11[1],
    condition = condition[1]
  )

#How many participants have taken art-classes?

length(art_interest$ID[art_interest$q11 == "yes" & art_interest$condition == 1])
length(art_interest$ID[art_interest$q11 == "yes" & art_interest$condition == 0])

art_interest$condition = as.factor(art_interest$condition)

art_interest$condition = plyr::revalue(art_interest$condition, c("1"= "Experts", "0"= "Non-Experts"))

all_part <- ggplot(art_interest, aes(x = q8)) +
  geom_bar(fill = "#99CCFF") +
  xlab("Ratings: Question X") +
  ylab("Participant counts") +
  theme_minimal()
  #How to change the values on the y-axis?

#Bar plots
bar_plot <- ggplot(art_interest, aes(x = q8)) + 
  geom_bar(fill = "#99CCFF") + 
  facet_wrap(~condition) + 
  xlab("Ratings: Question X") + 
  ylab("Partcipant counts") + 
  theme_minimal()

box_plot <- ggplot(art_interest,aes(y=q9,x=condition)) +
  geom_boxplot(color = "#336699", fill = "#6699CC") +
  xlab("Condition") +
  ylab("Rating") +
  ggtitle("Question X") + 
  coord_cartesian(ylim = c(1, 7)) +
  theme_minimal()

#Leaving an axis label blank: theme(axis.title.y = element_blank())

ggarrange(all_part,bar_plot) #what plots to display next to one another?

```

Testing art-interest

```{r}
#Mean and SD
art_interest %>%
  group_by(condition) %>%
  summarize(
    mean_q8 = round(mean(q8),2),
    sd_q8 = round(sd(q8),2),
    mean_q9 = round(mean(q9),2),
    sd_q9 = round(sd(q9),2),
    mean_q10 = round(mean(q10),2),
    sd_q10 = round(sd(q10),2)
  )

#testing assumptions - what to test?

model <- glm(condition ~ q8, family = 'binomial', art_interest) #one model per question or one model with all questions?
summary(model)


```

Scanpaths and heatmaps

```{r}
#Acessing quality of ET data?
#Subsetting dataframe to make heatmaps for 4 chosen images - two abs, two fig (one for each artist)

img <- png::readPNG('DataBsC/heatmaps_scanpaths_images/screenshot_fig11.png')
g <- grid::rasterGrob(img, interpolate = T)

jet.colors <- colorRampPalette(c("#00007F", "blue", "#007FFF", "cyan", "#7FFF7F", "yellow", "#FF7F00", "red", "#7F0000"))

#One participant, one image
heatmap_P1 <- ggplot(subset(Fix_df, ID==1 & image=='fig_11'),aes(x = PositionX, y = PositionY)) +
  xlim(0,1600) +
  ylim(0, 900) +
  annotation_custom(g, xmin=-Inf, xmax=Inf, ymin=-0, ymax=900) +
  stat_density2d(geom="raster", aes(fill=..density.., alpha=sqrt(sqrt(..density..))), contour=FALSE, n=1000) +
scale_alpha(range = c(0.1, 0.6)) + scale_fill_gradientn(colours = jet.colors(10), trans='sqrt')

averaged_full_data <- Fix_df %>%
  group_by(image) %>%
  mutate(Counter = sequence(rle(ID)$lengths)) %>%
  ungroup() %>%
  group_by(image, Counter) %>%
  summarize(
    PositionX = median(PositionX),
    PositionY = median(PositionY)
  )

#Heatmaps
aveHM <-
  ggplot(subset(averaged_full_data,image == "fig_11"),aes(x =PositionX, y = PositionY)) +
  xlim(0,1600) +
  ylim(0,900) +
  annotation_custom(g,xmin=-Inf, xmax=Inf, ymin=-0, ymax=900) +
  stat_density2d(geom="raster", aes(fill=..density.., alpha=sqrt(sqrt(..density..))), contour=FALSE, n=1000) + scale_alpha(range = c(0.1, 0.6)) +
  scale_fill_gradientn(colours = jet.colors(10), trans='sqrt') + ggtitle("All Participants")

#Scanpaths
aveSP = ggplot(subset(averaged_full_data, image == "fig_11"), aes(x = PositionX, y = PositionY)) +
  xlim(0,1600) +
  ylim(0,900) +
  annotation_custom(g, xmin=-Inf, xmax=Inf, ymin=-0, ymax=900) +
  geom_point(size = 8, alpha = 0.5, color = "white") + 
  geom_path(size = 1, alpha = 0.3) + 
  geom_text(aes(label = Counter, size = 5)) +
  ggtitle("All Participants")


#One participant
test_fix <- Fix_df %>%
  group_by(image) %>%
  mutate(Counter = sequence(rle(ID)$lengths))

SP = ggplot(subset(test_fix, image == "fig_11" & ID == 1), aes(x = PositionX, y = PositionY)) +
  xlim(0,1600) +
  ylim(0,900) +
  annotation_custom(g, xmin=-Inf, xmax=Inf, ymin=-0, ymax=900) +
  geom_point(size = 8, alpha = 0.5, color = "white") + 
  geom_path(size = 1, alpha = 0.3) + 
  geom_text(aes(label = Counter, size = 5)) +
  ggtitle("Participant X")

```

Cluster definition using DBSCAN

```{r}
#Dbscan should be on full data set?

averaged_full_data <- subset(Fix_df) %>%
  group_by(image) %>%
  mutate(Counter = sequence(rle(ID)$lengths)) %>%
  ungroup() %>%
  group_by(image, Counter) %>%
  summarize(
    PositionX = median(PositionX),
    PositionY = median(PositionY)
  )

#Generate kNN distance plots to determine optimal eps value - look for where the data changes significantly

kNN_df <- data.frame(image = numeric(),
                     optimal_eps = numeric())

for(i in unique(averaged_full_data$image)){
  kNN_df[nrow(kNN_df) + 1,] = c(image = i, optimal_eps = NA)
  data <- subset(averaged_full_data, image == i)
  data <- subset(data, select = c(PositionX, PositionY))
  matrix_data <- as.matrix(data)
  print(kNNdistplot(matrix_data,k=4))
}

#Change eps value accordingly
kNN_df$optimal_eps[1] = 42
kNN_df$optimal_eps[2] = 47
kNN_df$optimal_eps[3] = 40
kNN_df$optimal_eps[4] = 48
kNN_df$optimal_eps[5] = 49
kNN_df$optimal_eps[6] = 47
kNN_df$optimal_eps[7] = 49
kNN_df$optimal_eps[8] = 55
kNN_df$optimal_eps[9] = 46
kNN_df$optimal_eps[10] = 42
kNN_df$optimal_eps[11] = 49
kNN_df$optimal_eps[12] = 48
kNN_df$optimal_eps[13] = 45
kNN_df$optimal_eps[14] = 50
kNN_df$optimal_eps[15] = 48
kNN_df$optimal_eps[16] = 50
kNN_df$optimal_eps[17] = 49
kNN_df$optimal_eps[18] = 46
kNN_df$optimal_eps[19] = 48
kNN_df$optimal_eps[20] = 32
kNN_df$optimal_eps[21] = 49
kNN_df$optimal_eps[22] = 46
kNN_df$optimal_eps[23] = 45
kNN_df$optimal_eps[24] = 41
kNN_df$optimal_eps[25] = 40
kNN_df$optimal_eps[26] = 45
kNN_df$optimal_eps[27] = 43
kNN_df$optimal_eps[28] = 40
kNN_df$optimal_eps[29] = 42
kNN_df$optimal_eps[30] = 32
kNN_df$optimal_eps[31] = 42
kNN_df$optimal_eps[32] = 41
kNN_df$optimal_eps[33] = 43
kNN_df$optimal_eps[34] = 43
kNN_df$optimal_eps[35] = 45
kNN_df$optimal_eps[36] = 47
kNN_df$optimal_eps[37] = 40
kNN_df$optimal_eps[38] = 45
kNN_df$optimal_eps[39] = 49
kNN_df$optimal_eps[40] = 45

kNN_df$optimal_eps <- as.numeric(kNN_df$optimal_eps)

#Run cluster analysis using dbscan and save outcome
num = 1
for(i in unique(averaged_full_data$image)){
  data <- subset(averaged_full_data, image == i)
  data <- subset(data, select = c(PositionX, PositionY))
  matrix_data <- as.matrix(data)
  file = i
  db <- dbscan::dbscan(matrix_data, eps = kNN_df$optimal_eps[num], minPts = 3, borderPoints = FALSE)
  assign(paste("db_",file,sep = ""),db)
  num = num + 1
}

temp <- as.data.frame(db_fig_11$cluster) # 0 = noise, 1 = cluster - change db results accordingly
temp <- plyr::rename(temp, c('db_fig_11$cluster'= 'cluster')) #change db results accrodingly
temp$cluster <- as.factor(temp$cluster)
temp$cluster <- plyr::revalue(temp$cluster, c('0' = 'Noise','1'= 'Core'))

plot_data <- subset(averaged_full_data, averaged_full_data$image == 'fig_11', select = c(PositionX,PositionY)) #change data subset accordingly

plot_data <- cbind(plot_data,temp)

img <- png::readPNG('DataBsC/heatmaps_scanpaths_images/screenshot_fig11.png') #change png accordingly
g <- grid::rasterGrob(img, interpolate = T)

ggplot(plot_data, aes(x = PositionX, y = PositionY, color = cluster)) +
  xlim(0,1600) +
  ylim(0,900)+ 
  annotation_custom(g, xmin = 0, xmax = 1600, ymin = 0, ymax = 900) +
  geom_point(size = 1.5, shape = 'circle') +
  geom_mark_ellipse(data = subset(plot_data, plot_data$cluster == 'Core'),expand=0,aes(fill=cluster), show.legend = F)+
  #scale_color_brewer(palette = 'Greens', direction = 1)+
  scale_color_manual(values = wes_palette(n = 2, name ="Darjeeling1")) +
  ggtitle("'Fighter' by Egon Schiele") #change name and color scheme accordingly

#Other visualizations
#pairs(matrix_data, col = db$cluster + 1L) #clusters seperated by axis
#plot(matrix_data, col = db$cluster + 1L) #clusters = red, noise points = black
#points(matrix_data[db$cluster==0,], pch = 3, col = "grey")
```

Analysis and visualization of AUC data

```{r}

#These AUC scores was calculated from the 10 first fixations for each participant for each image
auc_df$condition <- as.factor(auc_df$condition)
auc_df$condition=plyr::revalue(auc_df$condition,c("0"="Non-experts","1"="Experts"))
auc_df$genre <- str_replace_all(auc_df$genre,"_","")

auc_5s$condition <- as.factor(auc_5s$condition)

#Plots
plot_data <- auc_df %>%
  group_by(condition, map_type,peak_group) %>%
  summarize(
    mean = mean(AUC),
    sd = sd(AUC),
    se = sd(AUC) / sqrt(length(AUC))
  )

pd <- position_dodge(0.5)

ggplot(plot_data, aes(x=condition, y=mean, colour=map_type)) + 
    geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.1, position = pd) +
    geom_line(position = pd) +
    geom_point(position = pd) +
    facet_wrap(~peak_group) +
    ylab('mean salience effects (AUCs)') +
    ggtitle('Salience effects for the first 10 fixations') +
    ylim(0.75,1) +
    scale_color_manual(values = wes_palette(n = 4, name ="GrandBudapest1"))

#Barplot - only for one type of plot
ggplot(subset(plot_data, plot_data$map_type == "combined"), aes(x = condition, y = mean, fill = condition)) + 
  geom_col() + 
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.1) +
  facet_wrap(~peak_group) +
  scale_fill_manual(values = wes_palette(n = 2, name = "GrandBudapest1")) +
  ggtitle('Salience effects for the first 10 fixations') +
  xlab('Condition') +
  ylab('mean salience effects (AUCs)') +
  guides(fill = "none")

#Over fixation index

auc_df$Fixation_Index <- as.numeric(auc_df$Fixation_Index)

#Full data set
plot_data <- subset(auc_df, auc_df$map_type == 'combined') %>%
  group_by(Fixation_Index,condition, genre,map_type, peak_group) %>%
  summarize(
    mean = mean(AUC),
    sd = sd(AUC),
    se = sd(AUC) / sqrt(length(AUC))
  )

plot_data$Fixation_Index <- as.character(plot_data$Fixation_Index)
#test_full$condition <- as.character(test_full$condition)

ggplot(subset(plot_data, plot_data$peak_group == 'few'), aes(x=Fixation_Index, y=mean, color = condition)) + 
    geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.1, position = pd) +
    geom_point(position = pd) +
    geom_line(aes(group = condition), position = pd) +
    xlab('fixation index') +
    ylab('mean salience effects (AUCs)') +
    ggtitle('Variation of salience effects over fixations') +
    ylim(0.7,1)+
    scale_x_discrete(limits=c("1","2","3","4","5","6","7","8","9","10"))+
    scale_color_manual(values = wes_palette(n = 2, name = "GrandBudapest1")) +
    facet_wrap(~genre)

ggplot(subset(plot_data, plot_data$peak_group == 'many'), aes(x=Fixation_Index, y=mean, color = condition)) + 
    geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.1, position = pd) +
    geom_point(position = pd) +
    geom_line(aes(group = condition), position = pd) +
    xlab('fixation index') +
    ylab('mean salience effects (AUCs)') +
    ggtitle('Variation of salience effects over fixations') +
    ylim(0.65,1)+
    scale_x_discrete(limits=c("1","2","3","4","5","6","7","8","9","10"))+
    scale_color_manual(values = wes_palette(n = 2, name = "GrandBudapest1")) +
    facet_wrap(~genre)


#Full data set - first five seconds
plot_data <- auc_5s %>%
  group_by(condition, map_type,peak_group) %>%
  summarize(
    mean = mean(AUC),
    sd = sd(AUC),
    se = sd(AUC) / sqrt(length(AUC))
  )

ggplot(plot_data, aes(x=condition, y=mean, colour=map_type)) + 
    geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.1, position = pd) +
    geom_line(position = pd) +
    geom_point(position = pd) +
    facet_wrap(~peak_group) +
    ylab('mean salience effects (AUCs)') +
    ggtitle('Salience effects for the first 10 fixations') +
    ylim(0.75,1) +
    scale_color_manual(values = wes_palette(n = 4, name ="GrandBudapest1"))

#Barplot - only for one type of plot
ggplot(subset(plot_data, plot_data$map_type == "combined"), aes(x = condition, y = mean, fill = condition)) + 
  geom_col() + 
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.1) +
  facet_wrap(~peak_group) +
  scale_fill_manual(values = wes_palette(n = 2, name = "GrandBudapest1")) +
  ggtitle('Salience effects for the first 10 fixations') +
  xlab('Condition') +
  ylab('mean salience effects (AUCs)') +
  guides(fill = "none")

plot_data <- subset(auc_5s, auc_5s$map_type == 'combined') %>%
  group_by(Fixation_Index,condition, genre,map_type, peak_group) %>%
  summarize(
    mean = mean(AUC),
    sd = sd(AUC),
    se = sd(AUC) / sqrt(length(AUC))
  )

plot_data$Fixation_Index <- as.character(plot_data$Fixation_Index)
#test_full$condition <- as.character(test_full$condition)

plot_data <- na.omit(plot_data)
plot_data <- subset(plot_data, plot_data$Fixation_Index != '14')

ggplot(subset(plot_data, plot_data$peak_group == 'few'), aes(x=Fixation_Index, y=mean, color = condition)) + 
    geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.1, position = pd) +
    geom_point(position = pd) +
    geom_line(aes(group = condition), position = pd) +
    xlab('fixation index') +
    ylab('mean salience effects (AUCs)') +
    ggtitle('Variation of salience effects over fixations') +
    ylim(0.7,1)+
    scale_x_discrete(limits=c("1","2","3","4","5","6","7","8","9","10"))+
    scale_color_manual(values = wes_palette(n = 2, name = "GrandBudapest1")) +
    facet_wrap(~genre)

ggplot(subset(plot_data, plot_data$peak_group == 'many'), aes(x=Fixation_Index, y=mean, color = condition)) + 
    geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.1, position = pd) +
    geom_point(position = pd) +
    geom_line(aes(group = condition), position = pd) +
    xlab('fixation index') +
    ylab('mean salience effects (AUCs)') +
    ggtitle('Variation of salience effects over fixations') +
    ylim(0.65,1)+
    scale_x_discrete(limits=c("1","2","3","4","5","6","7","8","9","10"))+
    scale_color_manual(values = wes_palette(n = 2, name = "GrandBudapest1")) +
    facet_wrap(~genre)

#stat_summary(fun = mean,geom="line",aes(group=1))

##Models

#Scale variables?
#rescalelist = c("AUC") #making a list with variales we want to scale
#auc_df.s = auc_df[, colnames(auc_df) %in% rescalelist] %>% 
>#  lapply(.,function(x) scale(x,center= mean(x,na.rm = T), scale = sd(x, na.rm = T)))%>% 
  #cbind(.,auc_df[,! colnames(auc_df) %in% rescalelist]) 


#time_df <- read.csv('combined_rocScores_variationOverFix.csv')
AUC_data_full$ID <- as.integer(AUC_data_full$ID)
AUC_data_full$genre <- as.factor(AUC_data_full$genre)
AUC_data_full$Fixation_Index <- factor(AUC_data_full$Fixation_Index, ordered = T)

subset_df <- subset(AUC_data_full, AUC_data_full$map_type == 'combined')


m1 <- lmer(AUC ~ 1 + condition*Fixation_Index*peak_group + 
             (1 + condition*Fixation_Index*peak_group|ID) + 
             (1 + condition*Fixation_Index*peak_group|image), 
           data = subset_df, 
           control = lmerControl(optimizer = "nloptwrap", calc.derivs = FALSE))

m2 <- lmer(AUC ~ 1 + condition*Fixation_Index*peak_group + (1|ID)+(1|image),data = subset_df)

```


